A Tufte Handout Example

### 2022-02-10 DraftRules.Rmd
html only for 3 docs and index

---
title: "Amberson Towers <br/> Condominum Council" # only for pdf output
subtitle: "Rules & Regulations" # only for html output
author: "Draft by Governance Committee"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
bibliography: skeleton.bib
link-citations: yes
---

>>>>

---
title: "Amberson Towers Condominum" # only for pdf output
subtitle: "Rules & Regulations" # only for html output
author: "Draft by Governance Committee"
date: "`r Sys.Date()`"
output:
  tufte::tufte_html: default
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

### 2022-02-10 index.Rmd
html only for 3 docs and index

---
title: "*Please Participate in Review Important <br/> Amberson Towers Condominium Documents*"
author: "A Request from the Governance Committee <br/> of the Amberson Towers Condominium Council"
date: "2/8/2022"
output: html_document
---

@@

### Please read these documents and comment

This document available in two formats. Choose the format you prefer:

* [*As an Adobe PDF document*](DraftRules.html)

* *As a web page*

>>>>

---
title: '*Time to Review Your Amberson<br/> Towers Condominium Bylaws*'
author: A Request from the Governance Committee to Review Important Governing Documents
date: —> By no later than XX February 2022 <—
output:
  html_document: default
  pdf_document: default
---

@@

#### *Why?*

The Governance Committee of the Amberson Towers Condominium (ATC) Council is reviewing three documents that “govern” how our shared community operates: our *Rules and Regulations*, a *Declaration for Amberson Towers*, and the *Amberson Towers Code of Regulations*.

These documents constitute the bylaws for shared governance by unit owners in ATC. Most of these documents were drafted in 1978 and tweaked a bit over the years^[View changes in the bylaws over time under the *Governance" tab at [https://www.ambersontowers.org/governance/](https://www.ambersontowers.org/governance/).] Many unit owners and the ATC Council recognize the need for revision and reformation of these bylaws and have identified many opportunities for improvement.

Perhaps you have recognized these and other needs and opportunities evident in the bylaws. Now is a chance to express your opinion.

ATC is your home. Owners are not renters. Owners *own* ATC. Owners can engage in the shared governance of ATC by providing feedback to the Governance Committee of the ATC about changes identified for the ATC bylaws.

#### *How?*

##### 1. Read the Documents.

Some of you received this note at your door or via the U.S. postal service. You may request printed versions of the documents and associated materials by contacting [Jim Donahoe](JDonahoe@meyersmanagement.com) in the Amberson Towers Management office. *However, if you have Internet access*, consider reviewing these documents online at https://davidpassmore.github.io/draft_rules/, as people receiving this note by email can.

Most of you received this note via email. Click on the following links to access web pages for each document^[View online or print to view offline]:

* [*Rules and Regulations*](DraftRules.html)

* [*Declaration for Amberson Tower*](DraftDeclare.html)

* [*Amberson Towers Code of Regulations*](DraftCode.html)

OK, so you won't be riveted to the page by the gripping prose in the documents. Yet, as U.S. Navy Admiral Hyman Rickover once wrote, “The Devil is in the details, but so is salvation.” Spend the time. The documents shape your ATC life.

##### 2. Offer Feedback

The right sidebar each document contains suggestions for revision identified by the Governance Committee. Consider those suggestions and assemble your own suggestions. Provide your feedback to the Committee in any of XXX ways:

* If you have Internet access, you may:

    + Complete and submit an online form at XXX(GOOGLE). Submit a form as many times as you wish as you reach new insights about bylaw revisions.

    + Offer your comments on the message board of the ATC online *Basecamp* account. Basecamp^[[Basecamp](https://basecamp.com/how-it-works) is a web-based project management tool that features to-do lists, milestone management, forum-like messaging, file sharing, and time tracking.] is a relatively easy-to-use online application that the ATV Council uses to manage its work. Over time, the ATC Basecamp application is likely to be adopted as a general and preferred tool communication among ATC owners.  Contact [Gil Citro](mailto:gil@ambersontowers.info) for an account.

* If your offline feedback:

    + Write your own comments and and submit them to the ATC Management office for delivery to the Governance Committee. You may write comments directly on printed copies of the documents.

    + Talk to provide your feedback with any of the following members of the Governance Committee, who ask the full Governance committee to integrate your comments and suggestions into the revised bylaws:
        + Gil Citro (contact info)
        + Gerry LaVan (contact info)
        + David Passmore (contact info)

#### *By When?*

For your feedback to be useful for the work of the Governance Committee, provide your feedback by XX February 2022.

#### *What's Next?*

The Governance Committee will review feedback from ATC owners and other consultation (e.g., legal), as necessary. Then, the Governance Committee will propose to the ATC Council the implementation of a ballot for owners to consider adoption of the revised bylaws.

### 2022-02-10 tuftetest.Rmd
html only for 3 docs and index

---
title: "Amberson Towers Condominum" # only for pdf output
subtitle: "Rules & Regulations" # only for html output
author: "Draft by Governance Committee"
date: "`r Sys.Date()`"
output:
  tufte::tufte_html: default
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

@@

## ARTICLE I

@@

## ARTICLE II

@@

BEGINNING on a point on the center line of Bayard Road, said point being located from the intersections of the northeast corner of the Winchester-Thurston School and the northeast side of Morewood Avenue the following courses; thence along the northeast side of Morewood Avenue N 14° 56' 35" W, a distance of 18.24' to a point; thence N 21° 13' 05" W, a distance of 60.22' to the center line of Bayard Road; thence the center line of Bayard Road N 68° 35' 55" E, a distance of 147.00' to the point of beginning; thence continuing along the said center line of Bayard Road N 68° 35' 55" E, a distance of 85.00' to a point of curvature; thence along an arc curving to the left having a radius of 60.00' and length of 103.91' **112.05'** to a point; thence N 67° 24' 05" E, a distance of 121.00' to a point; thence N 76° 35' 55" E, a distance of 37.00' to a point of curvature; thence by an arc curving to the left, having a radius of 80.00' and an arc length of 72.61' to a point; thence S 58° 21' 37" E, a distance of 54.82' to a point on the westerly line of Amberson Avenue; thence along the westerly line of Amberson Avenue, S 16° 03' 10" W, a distance of 144.00' to a point; thence continuing along the westerly line of Amberson Avenue S 24° 06' 20" E, a distance of 83.919' to a point of curvature; thence continuing along the westerly line of Amberson Avenue by an arc curving to the right, having a radius of 20.00' and an arc length of 34.63' to a point on the northerly line of Bayard Street; thence along the northerly line of Bayard Street, S 75° 05' 55" W, a distance of 211.50' to a point; thence N 14° 56' 35" W, a distance of 135.00' to a point; thence S 75° 05' 55" W, a distance of 99.77' to a point; thence N 14° 56' 35" W, a distance of 70.63' to a point; thence N 19° 00' 39" W, a distance of **87.40'** to the center of Bayard Road at the point of beginning.

@@

## ARTICLE III

The name by which the property is known is Amberson Towers.

## Article IV

### Section 1

The property consists of apartment units and common elements, as shown in a Declaration Plan prepared by J. J. Balobeck Associates, Registered Architects and recorded in the Office of the Recorder of Deeds of Allegheny County, Pennsylvania in Plan Book Volume 103, Pages 167 to 193 and is incorporated herein by reference.

### Section 2

  (a) The private elements of each respective unit shall include only the area within the boundary lines as described in Article IV, Section 2, paragraph (b) hereinbelow. Any adjacent or connecting porch or patio is a common element; provided, however, the owner of the connecting and adjacent unit shall have an exclusive easement for the private use thereof; and provided further the maintenance thereof shall be borne as provided in the Code of Regulations, Article X.

  (b) "Unit" means any numbered or lettered subdivision of the interior part of said building as shown on the Declaration Plans including the interior wall, ceiling and floor surfaces, which is designed or intended for a designated type of independent use, which has a direct exit to a common element or common elements leading to a public street or way and includes the proportionate undivided interest in the Common Elements which is assigned thereto by this Declaration or any amendments made hereto.

  (c) In the event that any Owner purchases two or more abutting condominium units, said Owner, at his own expense, shall have the right to obtain an easement or easements subject to the location of same by council, through such common elements, walls or floors in such location or locations as council shall determine to be safe and not injurious to the structure. In the event that thereafter said units again fall into separate ownership, any said easements are thereby extinguished and it shall be the obligation of owners to physically close said easements at their own expense but in accordance with plans and specifications of Council so as to bring said areas back into their original condition.

## ARTICLE V

### Section 1

The common elements consist of:

(a) The land on which the building is located and surrounding land;

(b) The foundations, structural parts, supports, main walls, roofs, basements, corridors, lobbies, stairways, entrances, and exits of the building.

(c) The yards, parking areas, driveways and outdoor recreation facilities.

(d) Portions of the land and building used exclusively for the management, operation or maintenance of the common elements; areas shown on declaration plan used for recreation or other common purposes.

(e) Installations of all central services and utilities, including but not limited to all water pipes, electric wires, general conduits and the like; but exclusive of the outlets thereof into each unit.

(f) All apparatus, equipment and installations existing for common use, including but not limited to elevators, elevator shafts, boilers and heaters and other heating apparatus, central air conditioners, water heaters and the like, and the individual blowers within the confines of each apartment.

(g) All other elements of the building necessary or convenient to its existence, management, operation, maintenance and safety or normally in common use.

(h) All conduits, wires and utility lines up to the outlets thereof inside the walls of each unit, regardless of location, and all bearing walls, columns, and beams together with all water heating equipment, foundations, pipes, ducts, flues, chutes, and other appurtenant insulation to the outlets regardless of location, parking stalls, caretaker and maintenance manager's apartment and storage lockers, if any.

(i) Garage and all ramps leading thereto.

### Section 2

>>>>

---
title: "A Tufte Handout Example"
runningheader: "Tufte Handout with R Markdown" # only for pdf output
subtitle: "An implementation in R Markdown" # only for html output
author: "JJ Allaire and Yihui Xie"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

@@

## ARTICLE I {-}

@@

## ARTICLE II {-}

@@

BEGINNING on a point on the center line of Bayard Road, said point being located from the intersections of the northeast corner of the Winchester-Thurston School and the northeast side of Morewood Avenue the following courses; thence along the northeast side of Morewood Avenue N 14° 56' 35" W, a distance of 18.24' to a point; thence N 21° 13' 05" W, a distance of 60.22' to the center line of Bayard Road; thence the center line of Bayard Road N 68° 35' 55" E, a distance of 147.00' to the point of beginning; thence continuing along the said center line of Bayard Road N 68° 35' 55" E, a distance of 85.00' to a point of curvature; thence along an arc curving to the left having a radius of 60.00' and length of ~~103.91'~~ **112.05'** to a point; thence N 67° 24' 05" E, a distance of 121.00' to a point; thence N 76° 35' 55" E, a distance of 37.00' to a point of curvature; thence by an arc curving to the left, having a radius of 80.00' and an arc length of 72.61' to a point; thence S 58° 21' 37" E, a distance of 54.82' to a point on the westerly line of Amberson Avenue; thence along the westerly line of Amberson Avenue, S 16° 03' 10" W, a distance of 144.00' to a point; thence continuing along the westerly line of Amberson Avenue S 24° 06' 20" E, a distance of 83.919' to a point of curvature; thence continuing along the westerly line of Amberson Avenue by an arc curving to the right, having a radius of 20.00' and an arc length of 34.63' to a point on the northerly line of Bayard Street; thence along the northerly line of Bayard Street, S 75° 05' 55" W, a distance of 211.50' to a point; thence N 14° 56' 35" W, a distance of 135.00' to a point; thence S 75° 05' 55" W, a distance of 99.77' to a point; thence N 14° 56' 35" W, a distance of 70.63' to a point; thence N 19° 00' 39" W, a distance of ~~87.30'~~ **87.40'** to the center of Bayard Road at the point of beginning.

@@

## ARTICLE V {-}

### Section 2 {-}
